MCC Novelty Kids

### 2019-02-05 stats/adults/visualizations.Rmd
update cogsci submission

d1 <- bind_rows(read_csv(file="novel.data.csv"),
               read_csv(file="pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         control = ifelse(change == "true", "true" , "false"))

d2 <- read_csv(file="inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

@@

dat <- bind_rows(read_csv(file="ex3.novel.data.csv"),
               read_csv(file="ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

dat %>%
  filter(alignment == "incongruent") %>%
  filter(correct_inf == correct_prior)

@@

ggplot() +
  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( ~ Experiment + Change) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#859900","#859900","#859900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
        panel.border = element_rect(color = "#859900", fill = NA, size = 6))

@@

```{r}
ggsave("graphs/data_ex3_round1.pdf", width = 6.5, height = 3, scale = 1.8)
```

@@

c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ggtitle("Experiment 3")+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F, size = 6)+
  #geom_smooth(method = "lm", se = F, col = "black", size =1)+
  theme_few(base_size = 20) + 
  guides(col = F)+
  scale_colour_viridis_d()
```

```{r}
ggsave("graphs/model_critique_ex3_round1.png", width = 4, height = 4, scale = 1)
```

@@

```{r}
ggsave("graphs/model_critique_ex3_round1_2.pdf", width = 10, height = 4, scale = 1.2)
```

>>>>

d1 <- bind_rows(read_csv(file="../data/novel.data.csv"),
               read_csv(file="../data/pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         control = ifelse(change == TRUE, "true" , "false"))

d2 <- read_csv(file="../data/inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"),
         control = ifelse(control == TRUE, "true" , "false"))

@@

dat <- bind_rows(read_csv(file="../data/ex3.novel.data.csv"),
               read_csv(file="../data/ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

@@

ggplot() +
  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( ~ Experiment + Change) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#859900","#859900","#859900"))

pdata <- p1 %>%
  multi_boot_standard(col = "correct")%>%
  mutate(Model = "Data")

pmd <- bind_rows(pdata, plot.model%>%
                   filter(Model == "Noisy RSA Model")%>%
                   ungroup()%>%
                   mutate(Prior = "Strong",
                          Model = "RSA Model"))

ggplot() +
  geom_jitter(data = p1, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = pmd, aes(x = Alignment, y = mean,col = Model, ymin = ci_lower, ymax = ci_upper),size = 1,  position = position_dodge(width = .5))+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( ~ Experiment + Change) +
  theme_few(base_size = 14) + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Condition",
                     breaks=c("Data","RSA Model"),
                     values= c("black","#859900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))

@@

```{r}
 ggsave("../graphs/Ex3_1_data_model_pred.pdf", width = 6.5, height = 3, scale = 1.3)
```

@@

c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  #ggtitle("Experiment 3")+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 4)+
  #geom_smooth(method = "lm", se = F, col = "black", size =1)+
  theme_few(base_size = ) + 
  guides(col = F)+
  scale_colour_viridis_d()
```

```{r}
ggsave("../graphs/model_critique_ex3_round1.png", width = 3, height = 3, scale = 1)
```

@@

```{r plotmodelcomp}

c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 12) + 
  guides(col = F)+
  scale_colour_viridis_d()

c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 12) + 
  scale_colour_manual(values = rev(viridis::viridis(3)))

pc3 <- data.frame(
    ex3 = pc1%>%pull(Data),
    ex3_ci_l = pc1%>%pull(Data_ci_low),
    ex3_ci_u = pc1%>%pull(Data_ci_up),
    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
    Prior = "Strong")

c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = ex3, y = ex4), inherit.aes = F, size = 3)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Data Experiment 3")+
  ylab("Data Experiment 4")+
  theme_few(base_size = 12)+ 
  scale_color_viridis_d()

ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T)

```{r}
ggsave("../graphs/overview_ex3_4.pdf", width = 10, height = 3, scale = 1)
```

### 2019-02-05 stats/kids/kids_inf_2.Rmd
add saves to cogsci folder
update cogsci submission

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date),
         experiment = "mcc_kids_inf_2_2")

@@

@@

write_csv(d, "data/kids_inf_2_data.csv")

>>>>

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date),
         experiment = "mcc_kids_inf_2_2",
         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))

@@

length(unique(log$subid))

sum(log$keep_drop=="drop")

@@

#write_csv(d, "data/kids_inf_2_data.csv")

### 2019-02-05 stats/kids/kids_model_predictions.Rmd
CogSci paper new template
update cogsci submission

```{r pretest data, include=FALSE}
pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
  filter(age != "2",
         trial_type != "train")%>%
  mutate(age_bin = factor(age),
         experiment = "preference_pretest",
         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
         agent = ifelse( change == "false", agent, altAgent),
         minage = min(age_num))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)

@@

@@

# model_pred<- webppl(
#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
#   data = pre_data,
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
# )

@@

@@

@@

@@

>>>>

```{r pretest data, include=FALSE}
pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
  filter(age != "2",
         trial_type != "train")%>%
  mutate(age_bin = factor(age),
         experiment = "preference_pretest",
         condition = ifelse(change == F, "same_speaker", "different_speaker"),
         agent = ifelse( change == F, agent, altAgent),
         minage = min(age_num))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)

@@

## Noisy model predictions

```{r}
noisyModelPredWebppl <- '

    var noise = uniformDrift({a: 0, b:1, width: 0.1})

    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)

    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))

    var rsaPredictions_diff_incong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality)

 var noisyRsaPredictions_diff_incong = expectation(addNoise(rsaPredictions_diff_incong, noise))

  var rsaPredictions_same_cong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality)

 var noisyRsaPredictions_same_cong = expectation(addNoise(rsaPredictions_same_cong, noise))

   var rsaPredictions_same_incong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality)

 var noisyRsaPredictions_same_incong = expectation(addNoise(rsaPredictions_same_incong, noise))

    return extend(
    // diff_speaker_params, same_speaker_params, 
      {
      diff_priorReg,
      same_priorReg,
      speakerOptimality,
      noisyRsaPredictions_diff_cong,
      noisyRsaPredictions_diff_incong,
      noisyRsaPredictions_same_cong,
      noisyRsaPredictions_same_incong,
      age_bin,
      so_slope,
      so_int,
      noise
    })

@@

model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

@@

```{r noisy combined model predictions}

noisy_model_pred <- readRDS("../saves/kids_noisy_model_predictions.rds")

noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

#saveRDS(noisy_model_pred, file = "../saves/kids_noisy_model_predictions.rds")

kids_noisy_model_pred <- noisy_model_pred%>%
  select(value) %>%
  map_df(bind_rows)%>%
  mutate(iteration = rep(1:8000,each = 40))%>%
  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
  gather(condition, prop_informative, -iteration,-age_bin,-noise)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))

@@

## Noisy RSA Model Predictions

  plot_noisy_model_pred <- kids_noisy_model_pred %>%
  group_by(model,age_bin,Speaker,Alignment)%>%
  summarise(mean = mean(prop_informative),
            lci = hdi_lower(prop_informative),
            uci = hdi_upper(prop_informative))

pred_noisy_plot <- ggplot(plot_noisy_model_pred)+
  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(y="Proportion Expected Choice")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  guides(col = F)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()
```

```{r, echo= F, fig.width= 10, fig.height = 8}
pred_noisy_plot
```

@@

#saveRDS(model_comp_mean_ci, "../saves/kids_model_comp_mean_ci.rds")

@@

# saveRDS(model_comp, "../saves/kids_model_comp.rds")

### 2019-02-05 stats/kids/kids_novel.Rmd
update cogsci submission

ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(condition~age)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

@@

ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
  geom_smooth(method = "loess", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
   facet_grid(condition ~.)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(condition~age)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c(F, T),
                     labels=c("No", "Yes"))
```

@@

ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
  geom_smooth(method = "lm", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
   facet_grid(condition ~.)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c(F, T),
                     labels=c("No", "Yes"))
```
